### 2024-09-02 NN/plots_latex.tex
commit

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots/Tanh2HiddenLayer-R2-vs-Num-of-Epochs-HiddenSize-12.png}
    \caption{Tanh2HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 12)}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots/Tanh2HiddenLayer-R2-vs-Num-of-Epochs-HiddenSize-20.png}
    \caption{Tanh2HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 20)}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots/Linear2HiddenLayer-R2-vs-Num-of-Epochs-HiddenSize-20.png}
    \caption{Linear2HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 20)}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots/Linear2HiddenLayer-R2-vs-Num-of-Epochs-HiddenSize-12.png}
    \caption{Linear2HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 12)}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots/Tanh1HiddenLayer-R2-vs-Num-of-Epochs-HiddenSize-10.png}
    \caption{Tanh1HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 10)}
\end{figure}

>>>>

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots/TanhReluFFNN-R2-vs-Num-of-Epochs-HiddenSize-12.png}
    \caption{TanhReluFFNN - R2 vs. Number of Epochs (Hidden Size: 12)}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots/TanhReluFFNN-R2-vs-Num-of-Epochs-HiddenSize-10.png}
    \caption{TanhReluFFNN - R2 vs. Number of Epochs (Hidden Size: 10)}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots/TanhReluFFNN-R2-vs-Num-of-Epochs-HiddenSize-20.png}
    \caption{TanhReluFFNN - R2 vs. Number of Epochs (Hidden Size: 20)}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots/TanhReluFFNN-R2-vs-Num-of-Epochs-HiddenSize-28.png}
    \caption{TanhReluFFNN - R2 vs. Number of Epochs (Hidden Size: 28)}
\end{figure}

### 2024-09-02 NN/plots_preds_latex.tex
commit

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots_preds/R2-98.65-TanhReluFFNN-conc.png}
    \caption{Prediction of conc with TanhReluFFNN epochs:50 - R-Squared: 0.99}
\end{figure}

>>>>

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots_preds/R2-99.30-TanhReluFFNN-Impedance-module.png}
    \caption{Prediction of Impedance module with TanhReluFFNN epochs:200 - R-Squared: 0.99}
\end{figure}
